FOODiE, Fortran Object oriented Ordinary Differential Equations integration library based on Abstract Calculus Pattern

### 2015-10-13 papers/announcement/manuscript.tex
Add low storage RK 2N s12/13/14o4
Add low storage RK 2N LSRK(12,4), LSRK(13,4) and LSRK(14,4) from
*High-accuracy large-step explicit Runge–Kutta (HALE-RK) schemes for
computational aeroacoustics*, Vasanth Allampalli and Ray Hixon and
M. Nallasamy and Scott D. Sawyer, Journal of Computational Physics,
vol. 228, 2009, pp. 3837--3850.

Why:

High number of stages increment stability locus.

This change addresses the need by:

Add new coefficients for ls_runge_kutta_interpolator class.

Side effects:

Update oscillation test and manuscript.

\begin{itemize}
  \item one-step schemes:
    \begin{itemize}
      \item explicit forward Euler scheme, it being $1^{st}$ order accurate;
      \item explicit Runge-Kutta schemes:
        \begin{itemize}
          \item TVD/SSP Runge-Kutta schemes:
            \begin{itemize}
              \item 2-stages, it being $2^{nd}$ order accurate;
              \item 3-stages, it being $3^{rd}$ order accurate;
              \item 5-stages, it being $4^{th}$ order accurate;
              \end{itemize}
          \item low storage Runge-Kutta schemes:
            \begin{itemize}
              \item 5-stages 2N registers schemes, it being $4^{th}$ order accurate;
              \item 6-stages 2N registers schemes, it being $4^{th}$ order accurate;
              \item 7-stages 2N registers schemes, it being $4^{th}$ order accurate;
              \end{itemize}
          \end{itemize}
      \end{itemize}
  \item multi-step schemes:
    \begin{itemize}
      \item explicit Adams-Bashforth schemes:
        \begin{itemize}
          \item 2-steps, it being $2^{nd}$ order accurate;
          \item 3-steps, it being $3^{rd}$ order accurate;
          \item 4-steps, it being $4^{th}$ order accurate;
          \end{itemize}
      \item implicit Adams-Moulton schemes:
        \begin{itemize}
          \item 1-step, it being $2^{nd}$ order accurate;
          \item 2-steps, it being $3^{rd}$ order accurate;
          \item 3-steps, it being $4^{th}$ order accurate;
          \end{itemize}
      \item predictor-corrector Adams-Bashforth-Moulton schemes:
        \begin{itemize}
          \item 1-step, it being $2^{nd}$ order accurate;
          \item 2-steps, it being $3^{rd}$ order accurate;
          \item 3-steps, it being $4^{th}$ order accurate;
          \end{itemize}
      \item explicit Leapfrog schemes\footnote{Leapfrog method is a 2-steps solver being, in general $2^{nd}$ order accurate, but mostly \emph{unstable}. It is well suited for periodic/oscillatory problems, thus the error is generally categorized accordingly to the phase and amplitude errors: the unfiltered scheme provides a $2^{nd}$ order error on phase approximation while the amplitude error is null. However, the unfiltered scheme is mostly unstable, thus many filters have been devised. In general, the filters retain the accuracy on the phase error, while affect the amplitude one.}:
        \begin{itemize}
          \item 2-steps unfiltered, it being $2^{nd}$ order accurate, but mostly \emph{unstable};
          \item 2-steps Robert-Asselin filtered, it being $1^{st}$ order accurate (on \emph{amplitude error});
          \item 2-steps Robert-Asselin-Williams filtered, it being $3^{rd}$ order accurate (on \emph{amplitude error});
          \end{itemize}
      \end{itemize}
  \end{itemize}

@@

Currently FOODiE provides 5/6/7 stages, all $4^{th}$ order, 2N registers explicit schemes, the coefficients of which are listed in tables \ref{tab:RK-ls-5}, \ref{tab:RK-ls-6} and \ref{tab:RK-ls-7}.

\begin{table}[!ht]
  \centering
  \caption{Williamson's table of 5 stages, $4^{th}$ order, Runge-Kutta low storage scheme\label{tab:RK-ls-5}}
  \resizebox{0.40\textwidth}{!}{%
  \begin{tabular}{cccc}
    Stage & $A$                                    & $B$                                    & $C$                                   \\
    \hline
    1     & $ 0                                  $ & $\frac{1432997174477}{9575080441755 }$ & $ 0                                 $ \\
    2     & $-\frac{567301805773 }{1357537059087}$ & $\frac{5161836677717}{13612068292357}$ & $\frac{1432997174477}{9575080441755}$ \\
    3     & $-\frac{2404267990393}{2016746695238}$ & $\frac{1720146321549}{2090206949498 }$ & $\frac{2526269341429}{6820363962896}$ \\
    4     & $-\frac{3550918686646}{2091501179385}$ & $\frac{3134564353537}{4481467310338 }$ & $\frac{2006345519317}{3224310063776}$ \\
    5     & $-\frac{1275806237668}{842570457699 }$ & $\frac{2277821191437}{14882151754819}$ & $\frac{2802321613138}{2924317926251}$ \\
  \end{tabular}}
\end{table}

\begin{table}[!ht]
  \centering
  \caption{Williamson's table of 6 stages, $4^{th}$ order, Runge-Kutta low storage scheme\label{tab:RK-ls-6}}
  \resizebox{0.40\textwidth}{!}{%
  \begin{tabular}{cccc}
    Stage & $A$               & $B$              & $C$              \\
    \hline
    1     & $ 0             $ & $0.122000000000$ & $0             $ \\
    2     & $-0.691750960670$ & $0.477263056358$ & $0.122000000000$ \\
    3     & $-1.727127405211$ & $0.381941220320$ & $0.269115878630$ \\
    4     & $-0.694890150986$ & $0.447757195744$ & $0.447717183551$ \\
    5     & $-1.039942756197$ & $0.498614246822$ & $0.749979795490$ \\
    6     & $-1.531977447611$ & $0.186648570846$ & $0.898555413085$ \\
  \end{tabular}}
\end{table}

\begin{table}[!ht]
  \centering
  \caption{Williamson's table of 7 stages, $4^{th}$ order, Runge-Kutta low storage scheme\label{tab:RK-ls-7}}
  \resizebox{0.40\textwidth}{!}{%
  \begin{tabular}{cccc}
    Stage & $A$               & $B$              & $C$              \\
    \hline
    1     & $ 0.000000000000$ & $0.117322146869$ & $0.000000000000$ \\
    2     & $-0.647900745934$ & $0.503270262127$ & $0.117322146869$ \\
    3     & $-2.704760863204$ & $0.233663281658$ & $0.294523230758$ \\
    4     & $-0.460080550118$ & $0.283419634625$ & $0.305658622131$ \\
    5     & $-0.500581787785$ & $0.540367414023$ & $0.582864148403$ \\
    6     & $-1.906532255913$ & $0.371499414620$ & $0.858664273599$ \\
    7     & $-1.450000000000$ & $0.136670099385$ & $0.868664273599$ \\
  \end{tabular}}
\end{table}

@@

\begin{table}[!ht]
  \centering
  \caption{Oscillation test: errors analysis of explicit Low Storage Runge-Kutta solvers}\label{tab:oscillation_errors_ls_rk}
  \begin{subtable}[b]{0.45\textwidth}
    \centering
    \caption{Low storage Runge-Kutta 1 stage}\label{tab:oscillation-ls-rk-1}
    \resizebox{1.00\textwidth}{!}{%
    \begin{tabular}{ccccc}
      \toprule
      {\sc Time Step} & {\sc Error X} & {\sc Error Y} & {\sc Order X} & {\sc Order Y} \\
      \hline
      5000.0          &  0.840E+10    &  0.706E+10    & /             & /             \\
      2500.0          &  0.503E+06    &  0.570E+06    & 14.03         & 13.60         \\
      1250.0          &  0.289E+04    &  0.272E+04    &  7.45         &  7.71         \\
       625.0          &  0.239E+03    &  0.232E+03    &  3.59         &  3.55         \\
       320.0          &  0.737E+02    &  0.722E+02    &  1.76         &  1.74         \\
       100.0          &  0.250E+02    &  0.247E+02    &  0.93         &  0.92         \\
      \bottomrule
    \end{tabular}}
  \end{subtable}\quad%
  \begin{subtable}[b]{0.45\textwidth}
    \centering
    \caption{Low storage Runge-Kutta 5 stages}\label{tab:oscillation-ls-rk-5}
    \resizebox{1.00\textwidth}{!}{%
    \begin{tabular}{ccccc}
      \toprule
      {\sc Time Step} & {\sc Error X} & {\sc Error Y} & {\sc Order X} & {\sc Order Y} \\
      \hline
      5000.0          &  0.120E+00    &  0.122E+00    & /             & /             \\
      2500.0          &  0.106E-01    &  0.107E-01    & 3.51          & 3.51          \\
      1250.0          &  0.935E-03    &  0.947E-03    & 3.50          & 3.50          \\
       625.0          &  0.826E-04    &  0.836E-04    & 3.50          & 3.50          \\
       320.0          &  0.793E-05    &  0.803E-05    & 3.50          & 3.50          \\
       100.0          &  0.135E-06    &  0.137E-06    & 3.50          & 3.50          \\
      \bottomrule
    \end{tabular}}
  \end{subtable}\\
  \begin{subtable}[b]{0.45\textwidth}
    \centering
    \caption{Low storage Runge-Kutta 6 stages}\label{tab:oscillation-ls-rk-s}
    \resizebox{1.00\textwidth}{!}{%
    \begin{tabular}{ccccc}
      \toprule
      {\sc Time Step} & {\sc Error X} & {\sc Error Y} & {\sc Order X} & {\sc Order Y} \\
      \hline
      5000.0          &  0.979E-01    &  0.994E-01    & /             & /             \\
      2500.0          &  0.876E-02    &  0.888E-02    & 3.48          & 3.48          \\
      1250.0          &  0.776E-03    &  0.786E-03    & 3.50          & 3.50          \\
       625.0          &  0.686E-04    &  0.695E-04    & 3.50          & 3.50          \\
       320.0          &  0.659E-05    &  0.667E-05    & 3.50          & 3.50          \\
       100.0          &  0.112E-06    &  0.114E-06    & 3.50          & 3.50          \\
      \bottomrule
    \end{tabular}}
  \end{subtable}\quad%
  \begin{subtable}[b]{0.45\textwidth}
    \centering
    \caption{Low storage Runge-Kutta 7 stages}\label{tab:oscillation-ls-rk-7}
    \resizebox{1.00\textwidth}{!}{%
    \begin{tabular}{ccccc}
      \toprule
      {\sc Time Step} & {\sc Error X} & {\sc Error Y} & {\sc Order X} & {\sc Order Y} \\
      \hline
      5000.0          &  0.238E-01    &  0.240E-01    & /             & /             \\
      2500.0          &  0.203E-02    &  0.205E-02    & 3.55          & 3.55          \\
      1250.0          &  0.177E-03    &  0.180E-03    & 3.51          & 3.51          \\
       625.0          &  0.156E-04    &  0.158E-04    & 3.50          & 3.50          \\
       320.0          &  0.150E-05    &  0.152E-05    & 3.50          & 3.50          \\
       100.0          &  0.269E-07    &  0.273E-07    & 3.46          & 3.46          \\
      \bottomrule
    \end{tabular}}
  \end{subtable}\\
\end{table}

@@

\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=1.00\textwidth]{errors-analysis/oscillation/errors_analysis-oscillation-ls-runge-kutta-1.png}
    \caption{1 stage}\label{fig:results-oscillation-ls-runge-kutta-1}
  \end{subfigure}\quad%
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=1.00\textwidth]{errors-analysis/oscillation/errors_analysis-oscillation-ls-runge-kutta-5.png}
    \caption{5 stages}\label{fig:results-oscillation-ls-runge-kutta-5}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=1.00\textwidth]{errors-analysis/oscillation/errors_analysis-oscillation-ls-runge-kutta-6.png}
    \caption{6 stages}\label{fig:results-oscillation-ls-runge-kutta-6}
  \end{subfigure}\quad%
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=1.00\textwidth]{errors-analysis/oscillation/errors_analysis-oscillation-ls-runge-kutta-7.png}
    \caption{7 stages}\label{fig:results-oscillation-ls-runge-kutta-7}
  \end{subfigure}
  \caption{Oscillation equations solutions computed by means of low storage Runge-Kutta solvers}\label{fig:results-oscillation-ls-runge-kutta}
\end{figure}

>>>>

\begin{itemize}
  \item one-step schemes:
    \begin{itemize}
      \item explicit forward Euler scheme, it being $1^{st}$ order accurate;
      \item explicit Runge-Kutta schemes:
        \begin{itemize}
          \item TVD/SSP Runge-Kutta schemes:
            \begin{itemize}
              \item 2-stages, it being $2^{nd}$ order accurate;
              \item 3-stages, it being $3^{rd}$ order accurate;
              \item 5-stages, it being $4^{th}$ order accurate;
              \end{itemize}
          \item low storage Runge-Kutta schemes:
            \begin{itemize}
              \item 5-stages 2N registers schemes, it being $4^{th}$ order accurate;
              \item 6-stages 2N registers schemes, it being $4^{th}$ order accurate;
              \item 7-stages 2N registers schemes, it being $4^{th}$ order accurate;
              \item 12-stages 2N registers schemes, it being $4^{th}$ order accurate;
              \item 13-stages 2N registers schemes, it being $4^{th}$ order accurate;
              \item 14-stages 2N registers schemes, it being $4^{th}$ order accurate;
              \end{itemize}
          \end{itemize}
      \end{itemize}
  \item multi-step schemes:
    \begin{itemize}
      \item explicit Adams-Bashforth schemes:
        \begin{itemize}
          \item 2-steps, it being $2^{nd}$ order accurate;
          \item 3-steps, it being $3^{rd}$ order accurate;
          \item 4-steps, it being $4^{th}$ order accurate;
          \end{itemize}
      \item implicit Adams-Moulton schemes:
        \begin{itemize}
          \item 1-step, it being $2^{nd}$ order accurate;
          \item 2-steps, it being $3^{rd}$ order accurate;
          \item 3-steps, it being $4^{th}$ order accurate;
          \end{itemize}
      \item predictor-corrector Adams-Bashforth-Moulton schemes:
        \begin{itemize}
          \item 1-step, it being $2^{nd}$ order accurate;
          \item 2-steps, it being $3^{rd}$ order accurate;
          \item 3-steps, it being $4^{th}$ order accurate;
          \end{itemize}
      \item explicit Leapfrog schemes\footnote{Leapfrog method is a 2-steps solver being, in general $2^{nd}$ order accurate, but mostly \emph{unstable}. It is well suited for periodic/oscillatory problems, thus the error is generally categorized accordingly to the phase and amplitude errors: the unfiltered scheme provides a $2^{nd}$ order error on phase approximation while the amplitude error is null. However, the unfiltered scheme is mostly unstable, thus many filters have been devised. In general, the filters retain the accuracy on the phase error, while affect the amplitude one.}:
        \begin{itemize}
          \item 2-steps unfiltered, it being $2^{nd}$ order accurate, but mostly \emph{unstable};
          \item 2-steps Robert-Asselin filtered, it being $1^{st}$ order accurate (on \emph{amplitude error});
          \item 2-steps Robert-Asselin-Williams filtered, it being $3^{rd}$ order accurate (on \emph{amplitude error});
          \end{itemize}
      \end{itemize}
  \end{itemize}

@@

Currently FOODiE provides 5/6/7/12/13/14 stages, all $4^{th}$ order, 2N registers explicit schemes, the coefficients of which are listed in table \ref{tab:RK-ls}.

\begin{table}[!ht]
  \centering
  \caption{Williamson's table of low storage Runge-Kutta schemes\label{tab:RK-ls}}
  \begin{subtable}[b]{0.45\textwidth}
    \centering
    \caption{5 stages, $4^{th}$ order\label{tab:RK-ls-5}}
    \resizebox{1.00\textwidth}{!}{%
    \begin{tabular}{cccc}
      Stage & $A$                                    & $B$                                    & $C$                                   \\
      \hline
      1     & $ 0                                  $ & $\frac{1432997174477}{9575080441755 }$ & $ 0                                 $ \\
      2     & $-\frac{567301805773 }{1357537059087}$ & $\frac{5161836677717}{13612068292357}$ & $\frac{1432997174477}{9575080441755}$ \\
      3     & $-\frac{2404267990393}{2016746695238}$ & $\frac{1720146321549}{2090206949498 }$ & $\frac{2526269341429}{6820363962896}$ \\
      4     & $-\frac{3550918686646}{2091501179385}$ & $\frac{3134564353537}{4481467310338 }$ & $\frac{2006345519317}{3224310063776}$ \\
      5     & $-\frac{1275806237668}{842570457699 }$ & $\frac{2277821191437}{14882151754819}$ & $\frac{2802321613138}{2924317926251}$ \\
    \end{tabular}}
  \end{subtable}\quad%
  \begin{subtable}[b]{0.45\textwidth}
    \centering
    \caption{6 stages, $4^{th}$ order\label{tab:RK-ls-6}}
    \resizebox{1.00\textwidth}{!}{%
    \begin{tabular}{cccc}
      Stage & $A$               & $B$              & $C$              \\
      \hline
      1     & $ 0             $ & $0.122000000000$ & $0             $ \\
      2     & $-0.691750960670$ & $0.477263056358$ & $0.122000000000$ \\
      3     & $-1.727127405211$ & $0.381941220320$ & $0.269115878630$ \\
      4     & $-0.694890150986$ & $0.447757195744$ & $0.447717183551$ \\
      5     & $-1.039942756197$ & $0.498614246822$ & $0.749979795490$ \\
      6     & $-1.531977447611$ & $0.186648570846$ & $0.898555413085$ \\
    \end{tabular}}
  \end{subtable}\\
  \begin{subtable}[b]{0.45\textwidth}
    \centering
    \caption{7 stages, $4^{th}$ order\label{tab:RK-ls-7}}
    \resizebox{1.00\textwidth}{!}{%
    \begin{tabular}{cccc}
      Stage & $A$               & $B$              & $C$              \\
      \hline
      1     & $ 0.000000000000$ & $0.117322146869$ & $0.000000000000$ \\
      2     & $-0.647900745934$ & $0.503270262127$ & $0.117322146869$ \\
      3     & $-2.704760863204$ & $0.233663281658$ & $0.294523230758$ \\
      4     & $-0.460080550118$ & $0.283419634625$ & $0.305658622131$ \\
      5     & $-0.500581787785$ & $0.540367414023$ & $0.582864148403$ \\
      6     & $-1.906532255913$ & $0.371499414620$ & $0.858664273599$ \\
      7     & $-1.450000000000$ & $0.136670099385$ & $0.868664273599$ \\
    \end{tabular}}
  \end{subtable}\quad%
  \begin{subtable}[b]{0.45\textwidth}
    \centering
    \caption{12 stages, $4^{th}$ order\label{tab:RK-ls-12}}
    \resizebox{1.00\textwidth}{!}{%
    \begin{tabular}{cccc}
      Stage & $A$                   & $B$                  & $C$                  \\
      \hline
      1     & $ 0.0000000000000000$ & $0.0650008435125904$ & $0.0000000000000000$ \\
      2     & $-0.0923311242368072$ & $0.0161459902249842$ & $0.0650008435125904$ \\
      3     & $-0.9441056581158819$ & $0.5758627178358159$ & $0.0796560563081853$ \\
      4     & $-4.3271273247576394$ & $0.1649758848361671$ & $0.1620416710085376$ \\
      5     & $-2.1557771329026072$ & $0.3934619494248182$ & $0.2248877362907778$ \\
      6     & $-0.9770727190189062$ & $0.0443509641602719$ & $0.2952293985641261$ \\
      7     & $-0.7581835342571139$ & $0.2074504268408778$ & $0.3318332506149405$ \\
      8     & $-1.7977525470825499$ & $0.6914247433015102$ & $0.4094724050198658$ \\
      9     & $-2.6915667972700770$ & $0.3766646883450449$ & $0.6356954475753369$ \\
      10    & $-4.6466798960268143$ & $0.0757190350155483$ & $0.6806551557645497$ \\
      11    & $-0.1539613783825189$ & $0.2027862031054088$ & $0.7143773712418350$ \\
      12    & $-0.5943293901830616$ & $0.2167029365631842$ & $0.9032588871651854$ \\
    \end{tabular}}
  \end{subtable}\\
  \begin{subtable}[b]{0.45\textwidth}
    \centering
    \caption{13 stages, $4^{th}$ order\label{tab:RK-ls-13}}
    \resizebox{1.00\textwidth}{!}{%
    \begin{tabular}{cccc}
      Stage & $A$                   & $B$                  & $C$                  \\
      \hline
      1     & $ 0.0000000000000000$ & $0.0271990297818803$ & $0.0000000000000000$ \\
      2     & $-0.6160178650170565$ & $0.1772488819905108$ & $0.0271990297818803$ \\
      3     & $-0.4449487060774118$ & $0.0378528418949694$ & $0.0952594339119365$ \\
      4     & $-1.0952033345276178$ & $0.6086431830142991$ & $0.1266450286591127$ \\
      5     & $-1.2256030785959187$ & $0.2154313974316100$ & $0.1825883045699772$ \\
      6     & $-0.2740182222332805$ & $0.2066152563885843$ & $0.3737511439063931$ \\
      7     & $-0.0411952089052647$ & $0.0415864076069797$ & $0.5301279418422206$ \\
      8     & $-0.1797084899153560$ & $0.0219891884310925$ & $0.5704177433952291$ \\
      9     & $-1.1771530652064288$ & $0.9893081222650993$ & $0.5885784947099155$ \\
      10    & $-0.4078831463120878$ & $0.0063199019859826$ & $0.6160769826246714$ \\
      11    & $-0.8295636426191777$ & $0.3749640721105318$ & $0.6223252334314046$ \\
      12    & $-4.7895970584252288$ & $1.6080235151003195$ & $0.6897593128753419$ \\
      13    & $-0.6606671432964504$ & $0.0961209123818189$ & $0.9126827615920843$ \\
    \end{tabular}}
  \end{subtable}\quad%
  \begin{subtable}[b]{0.45\textwidth}
    \centering
    \caption{14 stages, $4^{th}$ order\label{tab:RK-ls-14}}
    \resizebox{1.00\textwidth}{!}{%
    \begin{tabular}{cccc}
      Stage & $A$                   & $B$                  & $C$                  \\
      \hline
      1     & $ 0.0000000000000000$ & $0.0367762454319673$ & $0.0000000000000000$ \\
      2     & $-0.7188012108672410$ & $0.3136296607553959$ & $0.0367762454319673$ \\
      3     & $-0.7785331173421570$ & $0.1531848691869027$ & $0.1249685262725025$ \\
      4     & $-0.0053282796654044$ & $0.0030097086818182$ & $0.2446177702277698$ \\
      5     & $-0.8552979934029281$ & $0.3326293790646110$ & $0.2476149531070420$ \\
      6     & $-3.9564138245774565$ & $0.2440251405350864$ & $0.2969311120382472$ \\
      7     & $-1.5780575380587385$ & $0.3718879239592277$ & $0.3978149645802642$ \\
      8     & $-2.0837094552574054$ & $0.6204126221582444$ & $0.5270854589440328$ \\
      9     & $-0.7483334182761610$ & $0.1524043173028741$ & $0.6981269994175695$ \\
      10    & $-0.7032861106563359$ & $0.0760894927419266$ & $0.8190890835352128$ \\
      11    & $ 0.0013917096117681$ & $0.0077604214040978$ & $0.8527059887098624$ \\
      12    & $-0.0932075369637460$ & $0.0024647284755382$ & $0.8604711817462826$ \\
      13    & $-0.9514200470875948$ & $0.0780348340049386$ & $0.8627060376969976$ \\
      14    & $-7.1151571693922548$ & $5.5059777270269628$ & $0.8734213127600976$ \\
    \end{tabular}}
  \end{subtable}\\
\end{table}

@@

\begin{table}[!ht]
  \centering
  \caption{Oscillation test: errors analysis of explicit Low Storage Runge-Kutta solvers}\label{tab:oscillation_errors_ls_rk}
  \begin{subtable}[b]{0.45\textwidth}
    \centering
    \caption{1 stage}\label{tab:oscillation-ls-rk-1}
    \resizebox{1.00\textwidth}{!}{%
    \begin{tabular}{ccccc}
      \toprule
      {\sc Time Step} & {\sc Error X} & {\sc Error Y} & {\sc Order X} & {\sc Order Y} \\
      \hline
      5000.0          &  0.840E+10    &  0.706E+10    & /             & /             \\
      2500.0          &  0.503E+06    &  0.570E+06    & 14.03         & 13.60         \\
      1250.0          &  0.289E+04    &  0.272E+04    &  7.45         &  7.71         \\
       625.0          &  0.239E+03    &  0.232E+03    &  3.59         &  3.55         \\
       320.0          &  0.737E+02    &  0.722E+02    &  1.76         &  1.74         \\
       100.0          &  0.250E+02    &  0.247E+02    &  0.93         &  0.92         \\
      \bottomrule
    \end{tabular}}
  \end{subtable}\quad%
  \begin{subtable}[b]{0.45\textwidth}
    \centering
    \caption{5 stages}\label{tab:oscillation-ls-rk-5}
    \resizebox{1.00\textwidth}{!}{%
    \begin{tabular}{ccccc}
      \toprule
      {\sc Time Step} & {\sc Error X} & {\sc Error Y} & {\sc Order X} & {\sc Order Y} \\
      \hline
      5000.0          &  0.120E+00    &  0.122E+00    & /             & /             \\
      2500.0          &  0.106E-01    &  0.107E-01    & 3.51          & 3.51          \\
      1250.0          &  0.935E-03    &  0.947E-03    & 3.50          & 3.50          \\
       625.0          &  0.826E-04    &  0.836E-04    & 3.50          & 3.50          \\
       320.0          &  0.793E-05    &  0.803E-05    & 3.50          & 3.50          \\
       100.0          &  0.135E-06    &  0.137E-06    & 3.50          & 3.50          \\
      \bottomrule
    \end{tabular}}
  \end{subtable}\\
  \begin{subtable}[b]{0.45\textwidth}
    \centering
    \caption{6 stages}\label{tab:oscillation-ls-rk-6}
    \resizebox{1.00\textwidth}{!}{%
    \begin{tabular}{ccccc}
      \toprule
      {\sc Time Step} & {\sc Error X} & {\sc Error Y} & {\sc Order X} & {\sc Order Y} \\
      \hline
      5000.0          &  0.979E-01    &  0.994E-01    & /             & /             \\
      2500.0          &  0.876E-02    &  0.888E-02    & 3.48          & 3.48          \\
      1250.0          &  0.776E-03    &  0.786E-03    & 3.50          & 3.50          \\
       625.0          &  0.686E-04    &  0.695E-04    & 3.50          & 3.50          \\
       320.0          &  0.659E-05    &  0.667E-05    & 3.50          & 3.50          \\
       100.0          &  0.112E-06    &  0.114E-06    & 3.50          & 3.50          \\
      \bottomrule
    \end{tabular}}
  \end{subtable}\quad%
  \begin{subtable}[b]{0.45\textwidth}
    \centering
    \caption{7 stages}\label{tab:oscillation-ls-rk-7}
    \resizebox{1.00\textwidth}{!}{%
    \begin{tabular}{ccccc}
      \toprule
      {\sc Time Step} & {\sc Error X} & {\sc Error Y} & {\sc Order X} & {\sc Order Y} \\
      \hline
      5000.0          &  0.238E-01    &  0.240E-01    & /             & /             \\
      2500.0          &  0.203E-02    &  0.205E-02    & 3.55          & 3.55          \\
      1250.0          &  0.177E-03    &  0.180E-03    & 3.51          & 3.51          \\
       625.0          &  0.156E-04    &  0.158E-04    & 3.50          & 3.50          \\
       320.0          &  0.150E-05    &  0.152E-05    & 3.50          & 3.50          \\
       100.0          &  0.269E-07    &  0.273E-07    & 3.46          & 3.46          \\
      \bottomrule
    \end{tabular}}
  \end{subtable}\\
  \begin{subtable}[b]{0.45\textwidth}
    \centering
    \caption{12 stages}\label{tab:oscillation-ls-rk-12}
    \resizebox{1.00\textwidth}{!}{%
    \begin{tabular}{ccccc}
      \toprule
      {\sc Time Step} & {\sc Error X} & {\sc Error Y} & {\sc Order X} & {\sc Order Y} \\
      \hline
      5000.0          &  0.195E-01    &  0.198E-01    & /             & /             \\
      2500.0          &  0.175E-02    &  0.177E-02    & 3.48          & 3.48          \\
      1250.0          &  0.155E-03    &  0.157E-03    & 3.50          & 3.50          \\
       625.0          &  0.137E-04    &  0.139E-04    & 3.50          & 3.50          \\
       320.0          &  0.132E-05    &  0.133E-05    & 3.50          & 3.50          \\
       100.0          &  0.225E-07    &  0.228E-07    & 3.50          & 3.50          \\
      \bottomrule
    \end{tabular}}
  \end{subtable}\quad%
  \begin{subtable}[b]{0.45\textwidth}
    \centering
    \caption{13 stages}\label{tab:oscillation-ls-rk-13}
    \resizebox{1.00\textwidth}{!}{%
    \begin{tabular}{ccccc}
      \toprule
      {\sc Time Step} & {\sc Error X} & {\sc Error Y} & {\sc Order X} & {\sc Order Y} \\
      \hline
      5000.0          &  0.795E-02    &  0.805E-02    & /             & /             \\
      2500.0          &  0.703E-03    &  0.712E-03    & 3.50          & 3.50          \\
      1250.0          &  0.621E-04    &  0.629E-04    & 3.50          & 3.50          \\
       625.0          &  0.549E-05    &  0.556E-05    & 3.50          & 3.50          \\
       320.0          &  0.527E-06    &  0.534E-06    & 3.50          & 3.50          \\
       100.0          &  0.899E-08    &  0.911E-08    & 3.50          & 3.50          \\
      \bottomrule
    \end{tabular}}
  \end{subtable}\\
  \begin{subtable}[b]{0.45\textwidth}
    \centering
    \caption{14 stages}\label{tab:oscillation-ls-rk-14}
    \resizebox{1.00\textwidth}{!}{%
    \begin{tabular}{ccccc}
      \toprule
      {\sc Time Step} & {\sc Error X} & {\sc Error Y} & {\sc Order X} & {\sc Order Y} \\
      \hline
      5000.0          &  0.849E-02    &  0.860E-02    & /             & /             \\
      2500.0          &  0.750E-03    &  0.759E-03    & 3.50          & 3.50          \\
      1250.0          &  0.662E-04    &  0.671E-04    & 3.50          & 3.50          \\
       625.0          &  0.585E-05    &  0.593E-05    & 3.50          & 3.50          \\
       320.0          &  0.562E-06    &  0.569E-06    & 3.50          & 3.50          \\
       100.0          &  0.959E-08    &  0.972E-08    & 3.50          & 3.50          \\
      \bottomrule
    \end{tabular}}
  \end{subtable}\quad%
\end{table}

@@

\begin{figure}[!ht]
  \centering
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=1.00\textwidth]{errors-analysis/oscillation/errors_analysis-oscillation-ls-runge-kutta-1.png}
    \caption{1 stage}\label{fig:results-oscillation-ls-runge-kutta-1}
  \end{subfigure}\quad%
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=1.00\textwidth]{errors-analysis/oscillation/errors_analysis-oscillation-ls-runge-kutta-5.png}
    \caption{5 stages}\label{fig:results-oscillation-ls-runge-kutta-5}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=1.00\textwidth]{errors-analysis/oscillation/errors_analysis-oscillation-ls-runge-kutta-6.png}
    \caption{6 stages}\label{fig:results-oscillation-ls-runge-kutta-6}
  \end{subfigure}\quad%
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=1.00\textwidth]{errors-analysis/oscillation/errors_analysis-oscillation-ls-runge-kutta-7.png}
    \caption{7 stages}\label{fig:results-oscillation-ls-runge-kutta-7}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=1.00\textwidth]{errors-analysis/oscillation/errors_analysis-oscillation-ls-runge-kutta-12.png}
    \caption{12 stages}\label{fig:results-oscillation-ls-runge-kutta-12}
  \end{subfigure}\quad%
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=1.00\textwidth]{errors-analysis/oscillation/errors_analysis-oscillation-ls-runge-kutta-13.png}
    \caption{13 stages}\label{fig:results-oscillation-ls-runge-kutta-13}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=1.00\textwidth]{errors-analysis/oscillation/errors_analysis-oscillation-ls-runge-kutta-14.png}
    \caption{14 stages}\label{fig:results-oscillation-ls-runge-kutta-14}
  \end{subfigure}\quad%
  \caption{Oscillation equations solutions computed by means of low storage Runge-Kutta solvers}\label{fig:results-oscillation-ls-runge-kutta}
\end{figure}
